%============================= abstract.tex================================
\chapter*{Abstract}%
%\addcontentsline{toc}{chapter}{\numberline{}Abstract}%
\addcontentsline{toc}{chapter}{Abstract}%


A car rental service allows individuals to rent a vehicle for a short period of time, typically by the day or week. Customers can choose from a variety of vehicles, including economy cars, luxury vehicles. Rental services may be offered by traditional brick-and-mortar businesses, as well as online companies. Some car rental companies also offer additional services such as GPS rentals and insurance options. The purpose of a car rental service is to provide customers with a convenient and flexible transportation option for their travel needs.\\
The objective of this project is making an interactive user-friendly website which makes the registration of new cars, their modification, deletion in an effective, easy way. Every entity can be easily searched according to date of requirement. We have implemented the idea by making a web application that includes table visualization. Any staff using the website will be able to insert all the details, update and delete them when needed. The UI has been made very simple to provide ease of access for all types of users.\\
This project requires HTML, CSS in the frontend, Php for backend and database connectivity and MySQL for database management. We seek to expand the project by having a fully real-life model of the department in the college. 
\thispagestyle{plain}
%=======================================================================

