\chapter{Conclusion \& Future Enhancements}
\section{Conclusion}
A car rental management system is a software application that is designed to manage the operations of a car rental business. It typically includes features such as vehicle management, customer management, reservation management, billing and payment, and reporting.

The key entities in a car rental management system include vehicles, customers, reservations, rentals, billing and payment, and employees. These entities are typically stored in a relational database, such as MySQL, and accessed through a server-side scripting language, such as PHP.

The end user requirements for a car rental management system include easy and convenient booking, real-time availability, flexible rental options, multiple payment options, a user-friendly interface, security, and reporting.

The front-end of a car rental management system is typically created using a combination of HTML, CSS, and JavaScript, with the help of frameworks such as React, Angular, or Vue.js. The front-end communicates with the back-end to retrieve data from the database and display it to the user.

In conclusion, a car rental management system is a powerful tool that can automate and streamline the operations of a car rental business, making it more efficient and profitable. It is important to choose a system that meets the specific needs of your business and to implement it using best practices for security, performance, and scalability.
\pagebreak
\section{Future Enhancements}
There are several areas where car rental management services can be enhanced in the future:


1.Self-Service Kiosks: Self-service kiosks can be installed at the rental locations, allowing customers to quickly and easily rent cars without the need for human interaction.

2.Mobile App Integration: Car rental companies can develop mobile apps that allow customers to book cars, track their rental status, and make payments using their smartphones.

3.Automated Vehicle Management: Automated systems can be implemented to track the location, condition, and availability of rental cars in real-time, making it easier to manage the fleet and ensure that cars are always available for customers.

4.Predictive Maintenance: Predictive maintenance systems can be used to predict when a car will need maintenance and schedule it in advance, reducing downtime and keeping the fleet in top condition.

5.Advanced Payment Systems: Car rental companies can implement advanced payment systems that allow customers to make payments using various methods such as credit card, debit card, mobile wallet, and digital currencies.

6.Automated Return: Automated systems can be implemented to manage the return process of the cars, allowing customers to drop off their cars without having to interact with staff.

7.Virtual Reality: Virtual Reality can be used to give customers a virtual tour of the cars before renting them

